Stable Hot Spot Analysis (Draft)

### 2017-06-14 paper-main.tex
Updatet conclusion

\begin{abstract}
Hot spot analysis is essential for geo-statistics.
It supports decision making by detecting points
as well as areas of interest in comparison to their
neighbourhood. However, these methods are dependent
on different parameters, ranging from the resolution
of the study area to the size of their neighbourhood.
This dependence can lead to instabilities of the detected
hotspots, where the results can highly vary between
different parameters. A decision maker can therefore ask
how valid the analysis actually is.
%
In this study, we examine the impact of key parameters
on the stability of the hotspots, namely the size of
the neighbourhood, the resolution and the size of the
study area, as well as the influence of the ratio between
those parameters.
%
We compute the hotspots with the well known Getis-Ord ($G^*$)
statistic as well as its modification, the \emph{Focal $G^*$} statistic.
We measure the stability of the hotspot analysis using
a recently introduced \emph{stability of hotspots} metric (SoH)
and compare the results to intuitive visual analysis.
%
We evaluate the results on real world data with the well-known
yellow cab taxi data set from New York, Manhattan.
Our results indicate a negative impact on the stability with
an increase of the size of the neighbourhood as well as
a reduction of the size of the study area, regardless of
the resolution.
\end{abstract}

@@

Our results are based on the cab taxi data set from New York, Manhattan \cite{TODO}. 
We used only the dataset of January 2016. From that
dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
Zoom size 1 means we aggregate every point, which was in range of 100x100*0.000001 into one pixel. 
In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item The weight matrix W is from 3 to 43 with a stepsize of 4.
 \item The focal matrix F is from  17 to 125 with a stepsize of 12.
 \item The zoom level is from 1 to 5 with a stepsize of 1.
\end{itemize}
Therefore we calculate around 10*10*5=500 results for each fixed x.
The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.

@@

\section{Results}

@@

Blueline is Focal $G^*$. Redline is $G^*$

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward}
    \includegraphics[width=\linewidth]{images/SoHZoomUp}
    \label{fig:UpwardZoom}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward}
    \includegraphics[width=\linewidth]{images/SoHZoomDown}
    \label{fig:DownwardZoom}
  \end{subfigure}
  \caption{TODO}
  \label{fig:Zoom}
\end{figure}

The evaluation results are plotted in Fig.~\ref{fig:EvalResults}, each point in
the graph represents the \SOHUP metric (Eq.\ref{eq:SoH-up}) between two
$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
has a fixed size of $41{\times}41$

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward}
    \includegraphics[width=\linewidth]{images/SoHUpBlur}
    \label{fig:UpwardBlur}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward}
    \includegraphics[width=\linewidth]{images/SoHDownBlur}
    \label{fig:DownwardBlur}
  \end{subfigure}
  \caption{TODO}
  \label{fig:Blur}
\end{figure}

@@

@@

With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
All our results are based on the SoH. Further work should validate or improve this metric and compare if
Focal $G^*$ can have better results than $G^*$ in all dimension with fixed weight and focal size.

>>>>

\begin{abstract}
Hot spot analysis is essential for geo-statistics.
It supports decision making by detecting points
as well as areas of interest in comparison to their
neighbourhood. However, these methods are dependent
on different parameters, ranging from the resolution
of the study area to the size of their neighbourhood.
This dependence can lead to instabilities of the detected
hotspots, where the results can highly vary between
different parameters. A decision maker can therefore ask
how valid the analysis actually is.
%
In this study, we examine the impact of key parameters
on the stability of the hotspots, namely the size of
the neighbourhood, the resolution and the size of the
study area, as well as the influence of the ratio between
those parameters.
%
We compute the hotspots with the well known Getis-Ord ($G^*$)
statistic as well as its modification, the \emph{Focal $G^*$} statistic.
We measure the stability of the hotspot analysis using
a recently introduced \emph{stability of hotspots} metric (SoH)
and compare the results to intuitive visual analysis.
%
We evaluate the results on real world data with the well-known
yellow cab taxi data set from New York, Manhattan.
Our results indicate a negative impact on the stability with
a reduction of the size of the neighbourhood as well as
a reduction of the size of the study area, regardless of
the resolution.
\end{abstract}

@@

Our results are based on the cab taxi dataset from New York, Manhattan \cite{TODO}. 
We used only the dataset of January 2016. From that
dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
Zoom size 1 means we aggregate every point, which was in range of 100x100*0.000001 into one pixel. 
In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item The weight matrix W is from 3 to 43 with a stepsize of 4.
 \item The focal matrix F is from  17 to 125 with a stepsize of 12.
 \item The zoom level is from 1 to 5 with a stepsize of 1.
\end{itemize}
Therefore we calculate around $10 \cdot 10 \cdot 5=500$ results for each fixed x.
The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.

@@

@@

@@

TODO settings and images
The zoom level is a slice plane through our three dimensional space. 
TODO define parent child
The results can be found in figure ~\ref{fig:Zoom}.
For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
For the downward property, Focal $G^*$ leads to better results at zoom level 5.

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward for zoom}
    \includegraphics[width=\linewidth]{images/SoHZoomUp}
    \label{fig:UpwardZoom}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward for zoom}
    \includegraphics[width=\linewidth]{images/SoHZoomDown}
    \label{fig:DownwardZoom}
  \end{subfigure}
  \caption{SoH zoom}
  \label{fig:Zoom}
\end{figure}

The evaluation results are plotted in Fig.~\ref{fig:Blur}, each point in
the graph represents the \SOHUP metric (Eq.\ref{eq:SoH-up}) between two
$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
has a fixed size of $41{\times}41$

The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
Higher weight leads in general to better results for Focal $G^*$. $G^*$ doesn't fit to the mean of our whiskerplot.

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward for blur}
    \includegraphics[width=\linewidth]{images/SoHUpBlur}
    \label{fig:UpwardBlur}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward for blur}
    \includegraphics[width=\linewidth]{images/SoHDownBlur}
    \label{fig:DownwardBlur}
  \end{subfigure}
  \caption{SoH blur}
  \label{fig:Blur}
\end{figure}

@@

With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension around 0.6.
It can also lead to bad result, \SOHUP in the zoom dimension reaches nearly zero. Therefore we shown that it is important to have a metric
for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.
All our results are based on the SoH. Further work should validate or improve this metric.
